---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# LegoR

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/LegoR)](https://cran.r-project.org/package=LegoR)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![Travis build status](https://travis-ci.org/srvanderplas/LegoR.svg?branch=master)](https://travis-ci.org/srvanderplas/LegoR)
<!-- badges: end -->

The goal of LegoR is to make it easy to get Lego-centric data into R.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("srvanderplas/LegoR")
```

## Lego.com

The first set of functions provide a convenient way to scrape data from https://shop.lego.com/. 

The natural approach to gather data on all currently available lego sets is to get all sets by theme.
```{r}
(themes <- lego_get_themes())
```

Each theme link leads to a page with one or more sets. 

```{r}
library(tidyverse)
library(LegoR)
(architecture_sets <- lego_get_sets(themes$theme_link[1]))
```

If the goal is to get the price and titles, we could stop here, but more set data is available on the set-specific page.

```{r}
lego_get_set_data(architecture_sets$set_link[1])
```

These sets are structured in order to provide easy pipe functionality:
```{r}
set_data <- lego_get_themes() %>%
  filter(row_number() == 1) %>% # Don't get everything in the demo
  mutate(set_summary = purrr::map(theme_link, lego_get_sets)) %>%
  unnest(set_summary) %>%
  mutate(set_data = purrr::map(set_link, lego_get_set_data)) %>%
  unnest(set_data) %>%
  select(-set_Item) # Some variables are repeated

set_data
```