---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```
# LegoR

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/LegoR)](https://cran.r-project.org/package=LegoR)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![Travis build status](https://travis-ci.org/srvanderplas/LegoR.svg?branch=master)](https://travis-ci.org/srvanderplas/LegoR)
<!-- badges: end -->

The goal of LegoR is to make it easy to get Lego-centric data into R.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("srvanderplas/LegoR")
```
```{r}
# Set up and load packages
library(tidyverse)
library(LegoR)
```

## Lego.com

The first set of functions provide a convenient way to scrape data from https://shop.lego.com/. These functions are based on the `rvest` package and depend on the structure of the site; site updates may break the functionality. All functions for lego.com start with the `lego_` prefix.

The natural approach to gather data on all currently available lego sets is to get all sets by theme.
```{r}
(themes <- lego_get_themes())
```

Each theme link leads to a page with one or more sets. 

```{r}
(architecture_sets <- lego_get_sets(themes$theme_link[1]))
```

If the goal is to get the price and titles, we could stop here, but more set data is available on the set-specific page.

```{r}
lego_get_set_data(architecture_sets$set_link[1])
```

These sets are structured in order to provide easy pipe functionality:
```{r}
set_data <- lego_get_themes() %>%
  filter(row_number() == 1) %>% # Don't get everything in the demo
  mutate(set_summary = purrr::map(theme_link, lego_get_sets)) %>%
  unnest(set_summary) %>%
  mutate(set_data = purrr::map(set_link, lego_get_set_data)) %>%
  unnest(set_data) %>%
  select(-set_Item) # Some variables are repeated

set_data
```

## Brickset

https://brickset.com/ contains data on historical lego sets as well as current sets. Unlike Lego.com, we can access Brickset data using an API (application programming interface). This does require registering for a brickset account and requesting an API key. All functions for the brickset.com data start with the `brickset_` prefix.

```{r, eval = F}
brickset_setup() # guides you through the account setup process
```

Once you have your credentials, you can save them to your Rprofile using `brickset_save_credentials()`. This will also save the credentials as global variables. 

```{r, eval = F}
brickset_save_credentials("your_username", "your_password", "your_api_key")
```

Then, you can access brickset's data by authenticating. You may have to periodically reauthenticate depending on your internet configuration, but most functions should refresh the authentication automatically. 

```{r, eval = exists(".brickset_key")}
brickset_auth()
```

As with the Lego store, sets on brickset are organized by theme. 

```{r, eval = exists(".brickset_key")}
themes <- brickset_get_themes()
```

We can see what themes existed at the beginning...
```{r, eval = exists(".brickset_key")}
# Oldest themes
arrange(themes, yearfrom)
```

Or the themes that have been around the longest...
```{r, eval = exists(".brickset_key")}
# Longest running themes
arrange(themes, desc(yearto - yearfrom)) %>%
  head(10)
```

Most of the functions described in the [API documentation](https://brickset.com/tools/webservices/v2) have been wrapped; the exception is functions which concern a user's personal collection. 
