---
title: "Brickset Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Brickset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LegoR)
library(dplyr)
library(tidyr)
```


https://brickset.com/ contains data on historical lego sets as well as current sets. Unlike Lego.com, we can access Brickset data using an API (application programming interface). This does require registering for a brickset account and requesting an API key. All functions for the brickset.com data start with the `brickset_` prefix.

```{r, eval = F}
brickset_setup() # guides you through the account setup process
```

Once you have your credentials, you can save them to your Rprofile using `brickset_save_credentials()`. This will also save the credentials as global variables. 

```{r, eval = F}
brickset_save_credentials("your_username", "your_password", "your_api_key")
```

Then, you can access brickset's data by authenticating. You may have to periodically reauthenticate depending on your internet configuration, but most functions should refresh the authentication automatically. 

```{r, eval = exists(".brickset_key")}
brickset_auth()
```

As with the Lego store, sets on brickset are organized by theme. 

```{r, eval = exists(".brickset_key")}
themes <- brickset_get_themes()
```

We can see what themes existed at the beginning...
```{r, eval = exists(".brickset_key")}
# Oldest themes
arrange(themes, yearfrom)
```

Or the themes that have been around the longest...
```{r, eval = exists(".brickset_key")}
# Longest running themes
arrange(themes, desc(yearto - yearfrom)) %>%
  head(10)
```

Most of the functions described in the [API documentation](https://brickset.com/tools/webservices/v2) have been wrapped; the exception is functions which concern a user's personal collection. 

Some themes have sub-themes:

```{r, eval = exists(".brickset_key")}
# Themes with sub-themes
filter(themes, subthemecount > 0) %>%
  arrange(desc(subthemecount))
```

```{r, eval = exists(".brickset_key")}
(brickset_get_subthemes("Duplo"))
```

Not all themes are available in all years:
```{r, eval = exists(".brickset_key")}
(brickset_get_years("Pirates"))
```

We can get sets as well, searching using the set search api: https://brickset.com/api/v2.asmx?op=getSets
```{r, eval = exists(".brickset_key")}
brickset_auth() # At this point I had to reauthenticate
sets_2015 <- brickset_get_sets(year = 2015)
sets_2015
```

Note that the `setNumber` parameter is not equivalent to the lego set number, it is an internal Brickset number.
```{r, eval = exists(".brickset_key")}
(brickset_get_sets(setNumber = 71040))
(disney_castle <- brickset_get_sets(query = 71040))
```

We can also get reviews and instructions for a set:
```{r, eval = exists(".brickset_key")}
disney_castle_instructions <- brickset_get_instructions(disney_castle$setid)
```
The first link is [here](https://www.lego.com/biassets/bi/6194211.pdf) and shows the full instruction set for building a disney castle.

```{r, eval = exists(".brickset_key")}
disney_castle_reviews <- brickset_get_reviews(disney_castle$setid)

disney_castle_reviews %>% 
  gather(key = "ratingType", value = "ratingValue", overallrating:valueformoney) %>%
  mutate(ratingValue = factor(ratingValue)) %>%
  ggplot(aes(x = ratingType, fill = ratingValue)) + 
  geom_bar(position = "stack") + 
  scale_fill_brewer(palette = "BuGn")
```
